\documentclass[11pt]{article}

\author{Math 2420}
\date{Due Friday, March 21 by 5pm} 
\title{Homework 4}

\usepackage{graphicx,xypic}
\usepackage{amsthm}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\newtheorem{problem}{Problem}
\renewcommand*{\proofname}{{\color{blue}Solution}}


\setlength{\parindent}{0pt}
\setlength{\parskip}{1.25ex}


\begin{document}

\maketitle

% You are required to put your name here (this let's me know that you are submitting your own work):
{\bf\Large Your Name:} 

% You are required to put your collaborator names here:
Collaborator names: 


\vspace{.3in}
Topics covered: homotopy groups, H-groups, mapping spaces

Instructions: 
\begin{itemize}
\item This assignment must be submitted on Gradescope by the due date. 
\item If you collaborate with other students (which is encouraged!), please list your collaborators above. 
\item Homework is graded anonymously, so please avoid putting your name on every page of the assignment.
\item If you are stuck, please ask for help (from me or a classmate). Use Campuswire!  
\item You may freely use any fact proved in class (mention it in the appropriate spot). You should provide proof for facts that you use that were not proved in class. Usually you should be able to solve the problems without outside knowledge (sometimes I overlook some fact you may need, so please do ask if it seems like you need to use a significant result from another subject). 
\item Please try to make your solutions clear and concise. When grading, I will look to see that you have the correct idea, and also that you have addressed all of the main issues (for example, if you define a map on equivalence classes, you should say why it is well defined). That being said, I encourage you to try to restrict your solution to each problem to a single page. Often solutions can be even shorter than that. 
\end{itemize}
\pagebreak 



\pagebreak 
\begin{problem}
Assume $X,Y$ are path connected spaces. Fix $x_0\in X$ and $y_0,y_1\in Y$ and show the two definitions of $[X,Y]$ are the same. \footnote{Hint: use the homotopy extension property. Applying this probably requires some additional mild assumption on $X,Y$ (I will let you think about this).} 
\end{problem}


\begin{proof}

\end{proof}

\pagebreak 


\begin{problem}
Let $p:\tilde X\to X$ be the universal cover of a path connected space $X$. Show that $p$ induces an isomorphism on homotopy groups $\pi_k$ for $k\ge2$. 
\end{problem}

\begin{proof}

\end{proof} 


\pagebreak 
\begin{problem}For a based space $X$, $\Omega X$ denotes the loop space, and $c\in\Omega X$ denotes the constant map. Show that the map $\Omega X\rightarrow\Omega X$ defined by $\gamma\mapsto \gamma*c$ is homotopic to the identity, i.e.\ there is a homotopy $I\times \Omega X\to \Omega X$. \footnote{Remark: last semester you (probably) showed that $\gamma\simeq \gamma*c$ for each fixed $\gamma$. This is weaker than what is asked for here.}  \footnote{Remark: arguing similarly for associativity and inverses shows that $\Omega X$ is an $H$-group.} 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 
\begin{problem}
Let $A,B_1,B_2$ be based spaces. 
\begin{enumerate}[(a)]
\item Prove that $(B_1\times B_2)^A\cong B_1^A\times B_2^A$ (homeomorphism). 
\item Prove that $[A,B_1\times B_2]\cong[A,B_1]\times[A,B_2]$ (bijection of sets). 
\end{enumerate} 
\end{problem}

\begin{proof}

\end{proof}



\pagebreak 
\begin{problem}
Identify $X=\mathbb R P^\infty$ with the projectivization of the space of polynomials with coefficients in $\mathbb R$, and use this to define a monoid structure $m:X\times X\to X$. Show that the map $X\ni f\mapsto m(f,f)\in X$ is homotopic to a constant.\footnote{Hint: use the fundamental group, covering spaces.} Conclude that $\mathbb R P^\infty$ is an $H$-group. 
\end{problem}

\begin{proof}

\end{proof}





\end{document}