\documentclass[11pt]{article}

\author{Math 106}
\date{Due Friday, Dec 1 by 11:59pm} 
\title{Homework 10}

\usepackage{graphicx,xypic}
\usepackage{amsthm}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\newtheorem{problem}{Problem}
\renewcommand*{\proofname}{{\color{blue}Solution}}



\DeclareMathOperator{\sech}{sech}


\setlength{\parindent}{0pt}
\setlength{\parskip}{1.25ex}


\begin{document}

\maketitle

% You are required to put your name here:
{\bf\Large Name:} 


\vspace{.3in}
Topics covered: curvature, geodesic curvature, Gauss--Bonnet

Instructions: 
\begin{itemize}
\item This assignment must be submitted on Gradescope by the due date. 
\item If you collaborate with other students (which is encouraged!), please mention this near the corresponding problems. 
\item If you are stuck, please ask for help (from me, a TA, a classmate). Use ed discussions!  
\item You may freely use any fact proved in class. In general, you should provide proof for facts used that were not proved in class. 
\item Please restrict your solution to each problem to a single page. Usually solutions can be even shorter than that. If your solution is very long, you should think more about how to express it concisely.
\end{itemize}
\pagebreak 


\begin{problem}
Use HW9\#4 to compute the curvature of the hyperbolic plane. 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak

\begin{problem}
Let $T$ be a torus of revolution. Use the Gauss map to show, without using Gauss--Bonnet, that $\int_T K\>dA=0$. \footnote{Hint: You can do this with a ``soft" argument, i.e.\ one that does not involve heavy computation.} 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak

\begin{problem}
Prove that every embedding of a torus in $\mathbb R^3$ has points where the Gaussian curvature is positive, negative, and zero. 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak


\begin{problem}
True or false: the geodesic curvature $\kappa_g:=\alpha''\cdot (N\times\alpha')$ of a unit speed curve is intrinsic. \footnote{Hint: $\kappa^2=\kappa_g^2+\kappa_n^2$ and neither $\kappa$ nor $\kappa_n$ are intrinsic, so $\kappa_g$ should not be intrinsic.} \footnote{Hint: $\kappa_g$ is the projection of $\alpha''$ to the tangent space, so $\kappa_g$ should be intrinsic.} \footnote{Hint: the previous two hints are contradictory.} Give a rigorous proof\footnote{If it's not intrinsic, give an example. If it's intrinsic, express it in terms of the first fundamental form.} of your claim.
\end{problem}

\begin{proof}

\end{proof}

\pagebreak

\begin{problem}[Bonus]
Create a meme related to the course. Please post it to ed discussion for everyone's enjoyment. 
\end{problem}



\end{document}