\documentclass[11pt]{article}

\author{Math 106}
\date{Due Friday, Sept 15 by 5pm} 
\title{Homework 1}

\usepackage{graphicx,xypic}
\usepackage{amsthm}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\newtheorem{problem}{Problem}
\renewcommand*{\proofname}{{\color{blue}Solution}}


\setlength{\parindent}{0pt}
\setlength{\parskip}{1.25ex}


\begin{document}

\maketitle

% You are required to put your name here:
{\bf\Large Name:} 


\vspace{.3in}
Topics covered: curves, arclength

Instructions: 
\begin{itemize}
\item This assignment must be submitted on Gradescope by the due date. Gradescope Entry Code: XXV57E. 
\item If you collaborate with other students (which is encouraged!), please mention this near the corresponding problems. 
\item If you are stuck, please ask for help (from me, a TA, a classmate). Use Ed Discussion!  
\item You are free to use any fact proved in class. In general, you should provide proof for facts used that were not proved in class. 
\end{itemize}
\pagebreak 


\begin{problem}
Let $\alpha:I\to\mathbb R^3$ and $\beta:I\to\mathbb R^3$ be two curves. Let $\alpha\cdot\beta:I\to\mathbb R$ be the function defined by $(\alpha\cdot\beta)(t)=\alpha(t)\cdot\beta(t)$ (dot product). Prove that 
\[(\alpha\cdot\beta)'(t)=\alpha'(t)\cdot\beta(t)+\alpha(t)\cdot\beta'(t).\]
\end{problem}

\begin{proof}

\end{proof}

\pagebreak

\begin{problem}
Let $\alpha:I\to\mathbb R^3$ be a curve. Prove that $|\alpha(t)|$ is constant if and only if $\alpha(t)$ is orthogonal to $\alpha'(t)$ for all $t\in I$. 
\end{problem}

\begin{proof}

\end{proof} 

\pagebreak

\begin{problem}
Find a parameterized curve $\alpha:\mathbb R\to\mathbb R^2$ whose trace is the cycloid. Compute the length of one period of the cycloid.\footnote{Hint: at some point you may want to use the half-angle formula.}
\end{problem}

\begin{proof}

\end{proof}

\pagebreak

\begin{problem}
The curve $\alpha(t)=(e^{-t}\cos(t),e^{-t}\sin(t))$ for $t\in[0,\infty)$ is called the logarithmic spiral. Sketch this curve, and compute its length. 
\end{problem}

\begin{proof}

\end{proof}


\pagebreak 

\begin{problem}
Let $\alpha:[a,b]\to\mathbb R^3$ be a curve. Let $v$ be a unit vector. Prove that 
\[(\alpha(b)-\alpha(a))\cdot v=\int_a^b\alpha'(t)\cdot v\>dt\le\int_a^b|\alpha'(t)|\>dt.\]
Choose $v$ appropriately to deduce that the shortest path between any two points is a straight line. 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 


\begin{problem}
Fix a curve $\alpha:I\to\mathbb R^3$ and fix $[a,b]\subset I$. For a partition 
\[P=\{a=t_0<t_1<\cdots<t_n=b\},\] we defined $L(\alpha,P)=\sum|\alpha(t_{i+1})-\alpha(t_{i})|$ and $|P|=\max(t_{i+1}-t_{i})$. Prove that for each $\epsilon>0$, there exists $\delta>0$ so that if $|P|<\delta$, then 
\[\left|\int_a^b|\alpha'(t)|\>dt-L(\alpha,P)\right|<\epsilon.\]
\footnote{Suggestion: First replace $\int_a^b|\alpha'(t)|\>dt$ by a Riemann sum, and compare the Riemann sum to $L(\alpha,P)$. For the latter, it may help to use the mean value theorem for vector-valued functions (you will need to figure out which function to apply it to).} \footnote{This problem is probably harder than most HW problems for the course. Please ask questions if you are stuck. }
\end{problem}

\begin{proof}

\end{proof}





\end{document}