\documentclass[11pt]{article}

\author{Math 106}
\date{Due Friday, Oct 6 by 11:59pm} 
\title{Homework 4}

\usepackage{graphicx,xypic}
\usepackage{amsthm}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\newtheorem{problem}{Problem}
\renewcommand*{\proofname}{{\color{blue}Solution}}


\setlength{\parindent}{0pt}
\setlength{\parskip}{1.25ex}


\begin{document}

\maketitle

% You are required to put your name here:
{\bf\Large Name:} 


\vspace{.3in}
Topics covered: surfaces, tangent space

Instructions: 
\begin{itemize}
\item This assignment must be submitted on Gradescope by the due date. 
\item If you collaborate with other students (which is encouraged!), please mention this near the corresponding problems. 
\item If you are stuck, please ask for help (from me, a TA, a classmate). Use ed discussions!  
\item You may freely use any fact proved in class. In general, you should provide proof for facts used that were not proved in class. 
\item Please restrict your solution to each problem to a single page. Usually solutions can be even shorter than that. If your solution is very long, you should think more about how to express it concisely.
\end{itemize}
\pagebreak 


\begin{problem}
Show that the set $\{(x,y,z):x^2+y^2=1\}$ is a surface by covering it with coordinate charts. (What surface is this?)
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 

\begin{problem}
The equation $x^2+y^2-z^2=1$ defines a surface. Give a plot of this surface. Determine the tangent planes of the surface at the points $(x,y,0)$ and show that they are contain the $z$-axis. 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 

\begin{problem}
Let $N=(0,0,1)\in S^2$ be the north pole. Define stereographic projection $\pi: S^2\setminus\{N\}\to \mathbb R^2$ as follows. Given $p=(x,y,z)$, define $\pi(p)$ as the intersection of the line between $N$ and $p$ with the $xy$-plane. Determine a formula for the inverse of $\pi$. \footnote{Hint: Given $(u,v)\in\mathbb R^2$, find a formula for the line between $(u,v,0)$ and $(0,0,1)$ and compute the intersection of this line with $S^2$.} \footnote{This problem gives yet another way to cover the sphere by coordinate charts.} 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 

\begin{problem}
Let $\alpha:[0,1]\to\mathbb R^2$ be a plane curve that lies in the right-half plane and meets the $y$ axis at its endpoints $\alpha(0),\alpha(1)$. What conditions should $\alpha$ satisfy to ensure that the set obtained by rotating this curve about the $y$-axis is a surface? Your explanation should be rigorous.
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 

\begin{problem}
Give a coordinate system for the M\"obius strip. Do the same for an annulus with two twists. Include an image of your surfaces, plotted using \texttt{ParametricPlot3D} in Mathematica, or similar. 
\end{problem}


\begin{proof}

\end{proof}

\pagebreak 


\begin{problem}[Bonus]
Form a surface by gluing two cylinders along a square in such a way that the central curves of the two cylinders meet at a right angle. Cut each cylinder down the middle. What is the result? Repeat with gluing a cylinder and a M\"obius band, and with gluing two M\"obius bands. Include pictures of the results.
\end{problem}

\begin{proof}

\end{proof}




\end{document}