\documentclass[11pt]{article}

\author{Math 2420}
\date{Due Friday, April 12 by 5pm} 
\title{Homework 9}

\usepackage{graphicx,xypic}
\usepackage{amsthm}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\newtheorem{problem}{Problem}
\renewcommand*{\proofname}{{\color{blue}Solution}}


\newcommand{\Ext}{Ext}
\newcommand{\Hom}{Hom}
\newcommand{\Z}{\mathbb Z}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.25ex}


\begin{document}

\maketitle

% You are required to put your name here:
{\bf\Large Your Name:} 

Collaborator names: 


\vspace{.3in}
Topics covered: cohomology, Tor groups, K\"unneth theorem, acyclic models

Instructions: 
\begin{itemize}
\item This assignment must be submitted on Gradescope by the due date. 
\item If you collaborate with other students (encouraged!), please list your collaborators above. 
\item If you are stuck, please ask for help (from me or a classmate). Use Campuswire!  
\item You may freely use any fact proved in class. Usually you should be able to solve the problems without outside knowledge. You should provide proof for facts that you use that were not proved in class. 
\item Please restrict your solution to each problem to a single page. Usually solutions can be even shorter than that. If your solution is very long, you should think more about how to express it concisely.
\end{itemize}
\pagebreak 


\begin{problem}
Let $X,Y$ be cell complexes, and give $X\times Y$ the product cell structure. Prove (with care!)\footnote{I did this without care in class. Do better!} that $C_*(X\times Y)$ and $C_*(X)\otimes C_*(Y)$ are isomorphic chain complexes. 
\end{problem}

\begin{proof}

\end{proof}


\pagebreak 


\begin{problem}
Show that Tor$(A,\mathbb Q/\mathbb Z)$ is the torsion subgroup of $A$. Deduce that $A$ is torsion free if and only if Tor$(A,B)=0$ for all $B$. 
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 


\begin{problem}
Prove that Euler characteristic of compact spaces is multiplicative 
\[\chi(X\times Y)=\chi(X)\chi(Y),\] where $\chi(X)=\sum(-1)^i\beta_i$ and $\beta_i$ is the rank of $H_i(X)$ (known as the $i$-th Betti number).
\end{problem}

\begin{proof}

\end{proof}

\pagebreak 


\begin{problem}
Fix $n$, and let $X_d$ be the space obtained from attaching an $n$-cell to $S^{n-1}$ by a map of degree $d$. Use K\"unneth to compute the homology of $X_d\times X_{d'}$ for any $d,d'$. \footnote{The answer should be an (explicit) abelian group that depends on $d,d'$.} 
\end{problem}

\begin{proof}

\end{proof}


\pagebreak 

\begin{problem}
Use acyclic models to prove that any two natural chain maps $\phi,\psi:S_*(X)\otimes S_*(Y)\to S_*(X)\otimes S_*(Y)$ that agree in degree $0$ are chain homotopy equivalent. 
\end{problem}

\begin{proof}

\end{proof}






\end{document}