\documentclass[11pt]{article}

\author{Math 2420}
\date{Due Friday, April 5 by 5pm} 
\title{Homework 8}

\usepackage{graphicx,xypic}
\usepackage{amsthm}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\newtheorem{problem}{Problem}
\renewcommand*{\proofname}{{\color{blue}Solution}}


\setlength{\parindent}{0pt}
\setlength{\parskip}{1.25ex}


\begin{document}

\maketitle

% You are required to put your name here:
{\bf\Large Your Name:} 

Collaborator names: 


\vspace{.3in}
Topics covered: cohomology, universal coefficients, Ext groups

Instructions: 
\begin{itemize}
\item This assignment must be submitted on Gradescope by the due date. 
\item If you collaborate with other students (encouraged!), please list your collaborators above. 
\item If you are stuck, please ask for help (from me or a classmate). Use Campuswire!  
\item You may freely use any fact proved in class. Usually you should be able to solve the problems without outside knowledge. You should provide proof for facts that you use that were not proved in class. 
\item Please restrict your solution to each problem to a single page. Usually solutions can be even shorter than that. If your solution is very long, you should think more about how to express it concisely.
\end{itemize}
\pagebreak 


\pagebreak 


\begin{problem}
Regarding $\mathbb Z/2\mathbb Z$ as a module over $\mathbb Z/4\mathbb Z$, construct a resolution of $\mathbb Z/2\mathbb Z$ by free modules over $\mathbb Z/4\mathbb Z$ and use this to show that $Ext_{\mathbb Z/4\mathbb Z}^k(\mathbb Z/2\mathbb Z,\mathbb Z/2\mathbb Z)$ is nonzero for each $k$. 
\end{problem}

\begin{proof}

\end{proof} 


\pagebreak 



\begin{problem}
Compute $H^i(S^n;M)$ by induction on $n$ in two ways: once using the LES of a pair and once using Mayer--Vietoris (for cohomology). 
\end{problem}

\begin{proof}

\end{proof} 


\pagebreak 



\begin{problem}
Show if $f:S^n\to S^n$ has degree $d$, then $f^*:H^n(S^n;M)\to H^n(S^n;M)$ is multiplication by $d$. 
\end{problem}

\begin{proof}

\end{proof} 


\pagebreak 



\begin{problem}
Prove $H^1(X;\mathbb Z)$ and $[X,S^1]$ are naturally isomorphic groups (where the group structure on $[X,S^1]$ comes from the fact that $S^1$ is a group). \footnote{Hint: you did part of the work in proving this on the last assignment. You should start by figuring out what is left to do. Be sure to read the problem statement carefully.} 
\end{problem}

\begin{proof}

\end{proof}

\end{document}